% Page 43 demo translation (RU/EN/ZH/JA) — quick pass
\documentclass[11pt]{article}

\usepackage[a4paper,margin=1.5cm]{geometry}
\usepackage{fontspec}
\usepackage{xeCJK}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{url}

\setmainfont{Noto Serif}
\setsansfont{Noto Sans}
\setCJKmainfont{Noto Serif CJK SC}
\newCJKfontfamily\CJKjp{Noto Serif CJK JP}

\definecolor{enblue}{HTML}{1E5AA8}
\definecolor{zhred}{HTML}{B01E1E}
\definecolor{jagreen}{HTML}{167A3A}

\newcommand{\ru}[1]{\textcolor{black}{#1}}
\newcommand{\en}[1]{\textcolor{enblue}{#1}}
\newcommand{\zh}[1]{\textcolor{zhred}{#1}}
\newcommand{\ja}[1]{{\CJKjp\textcolor{jagreen}{#1}}}

\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*,itemsep=0.55em}
\linespread{1.03}

\begin{document}

{\large \textbf{Page 43 — Demo translation}}\par
\vspace{0.6em}

\begin{itemize}
  \item \ru{…предложили купить базу данных, от которой я, разумеется, отказался.}
  
        \en{…they offered to sell me a database, which I of course refused.}
  
        \zh{……他们提出要卖给我一份数据库，我当然拒绝了。}
  
        \ja{……データベースを買えと持ちかけられたが、もちろん断った。}

  \item \ru{Но я отказался, а кто-то согласится.}
  
        \en{But I refused—and someone else will accept.}
  
        \zh{我拒绝了，但总会有人答应。}
  
        \ja{しかし私は断っても、誰かは応じるだろう。}

  \item \ru{Почему предложили мне – я один из создателей проекта ВКонтакте.ру.}
  
        \en{Why did they come to me? Because I’m one of the creators of the VKontakte.ru project.}
  
        \zh{为什么找上我？因为我是 Vkontakte.ru 项目的共同创始人之一。}
  
        \ja{なぜ私に持ちかけたのか――私はVKontakte.ruプロジェクトの創設者の一人だからだ。}

  \item \ru{Этот сайт, как и moifakultet, является клоном американского сайта facebook.com, однако мы создаем наш, российский сайт со своей спецификой и рядом функций.}
  
        \en{This site—like moifakultet—is a clone of the American site facebook.com; however, we’re building our own Russian site, with its own quirks and a set of features.}
  
        \zh{这个网站和 moifakultet 一样，都是美国网站 facebook.com 的“克隆”，但我们在做的是一个有本土特色、带一系列功能的俄罗斯网站。}
  
        \ja{このサイトもmoifakultetも米国のfacebook.comのクローンだが、私たちは独自の仕様と機能を備えたロシア版のサイトを作っている。}

  \item \ru{Если вас заинтересовал moifakultet, но вам не нравятся баги, слабая функциональность, корявость в альтернативных браузерах и т. д., я советую использовать ВКонтакте.ру.}
  
        \en{If moifakultet interested you but you’re tired of bugs, weak functionality, awkward behavior in nonstandard browsers, etc., I recommend using VKontakte.ru.}
  
        \zh{如果你对 moifakultet 感兴趣，但又受不了它的 bug、功能孱弱、在非主流浏览器里各种别扭等等，我建议你用 Vkontakte.ru。}
  
        \ja{moifakultetに興味はあるが、バグや貧弱な機能、別ブラウザでの不格好さ等が気になるなら、VKontakte.ruを使うことを勧める。}

  \item \ru{Друзья, если вы посмотрите сайт и согласитесь, что vkontakte.ru – проект более серьезный и профессиональный, прошу пригласить туда друзей и предупредить их о том, о чем я рассказал.}
  
        \en{Friends, if you look at the site and agree that vkontakte.ru is a more serious, professional project, please invite your friends there and warn them about what I’ve described.}
  
        \zh{朋友们，如果你们看过网站后也同意 vkontakte.ru 是个更严肃、更专业的项目，请邀请朋友加入，并提醒他们我说过的这些事。}
  
        \ja{みなさん、サイトを見てvkontakte.ruのほうがより真剣でプロフェッショナルなプロジェクトだと同意できるなら、友人を招待し、私が話したことを伝えてほしい。}

  \item \ru{Для всех нас очень важна ваша поддержка – без нее проект и все наши старания бессмысленны.}
  
        \en{Your support is extremely important to all of us—without it, the project and all our effort are meaningless.}
  
        \zh{你们的支持对我们所有人都非常重要——没有它，这个项目和我们的一切努力都毫无意义。}
  
        \ja{皆さんの支援は私たち全員にとって極めて重要だ。それがなければ、プロジェクトも私たちの努力も無意味になる。}

  \item \ru{Пожалуйста, напишите, что вы думаете об этом.}
  
        \en{Please write what you think about this.}
  
        \zh{请写下你们的看法。}
  
        \ja{ぜひ意見を書いてほしい。}

  \item \ru{Автор: durov 4.12.2006, 7:44}
  
        \en{Author: durov — 2006-12-04 07:44}
  
        \zh{作者：durov　2006-12-04 07:44}
  
        \ja{投稿者：durov　2006-12-04 07:44}

  \item \ru{UPDATE!}
  
        \en{UPDATE!}
  
        \zh{更新！}
  
        \ja{追記！}

  \item \ru{Только что мне рассказали, что администратор сайта moifakultet.ru теперь обвиняет нас в том, что мы его якобы злостно взломали.}
  
        \en{I’ve just been told that the admin of moifakultet.ru is now accusing us of having maliciously hacked them.}
  
        \zh{刚刚有人告诉我，moifakultet.ru 的管理员现在指控我们“恶意入侵”了他们的网站。}
  
        \ja{たった今、moifakultet.ruの管理者が、私たちが悪質にハッキングしたと非難していると聞いた。}

  \item \ru{Приехали, называется…}
  
        \en{Well, that’s just great…}
  
        \zh{真是离谱……}
  
        \ja{まったく、やってられない……}

  \item \ru{Мы сотрудничаем с серьезной командой по информационной безопасности, которая с нами работала некоторое время, – они не занимаются нелегалом.}
  
        \en{We work with a serious information-security team that collaborated with us for a while—they don’t do illegal stuff.}
  
        \zh{我们曾和一支靠谱的信息安全团队合作过一段时间——他们不干违法的事。}
  
        \ja{私たちはしばらくの間、きちんとした情報セキュリティのチームと協力していたが、彼らは違法行為には手を出さない。}

  \item \ru{Как оказалось, moifakultet взломали хакеры, которые как-то узнали о работе над параллельными проектами и решили «через них» подзаработать.}
  
        \en{As it turns out, moifakultet was hacked by hackers who somehow learned about the parallel projects and decided to make some money “through them.”}
  
        \zh{事实证明，moifakultet 是被黑客攻破的：他们不知怎么得知我们在做彼此平行的项目，就想“借此”捞一笔。}
  
        \ja{実際には、moifakultetはハッカーに侵入されていた。彼らは並行して進むプロジェクトのことを何らかの形で知り、「それを通じて」ひと稼ぎしようとしたのだ。}

  \item \ru{Продать дыры одного сайта владельцу другого и наоборот.}
  
        \en{Sell the vulnerabilities of one site to the owner of the other—and vice versa.}
  
        \zh{把一个网站的漏洞卖给另一个网站的站长，反过来也一样。}
  
        \ja{片方のサイトの脆弱性をもう片方の運営者に売り、逆もまた同様に。}

  \item \ru{Они связались через нашу команду со мной и предложили купить БД незадачливого конкурента.}
  
        \en{They reached me through our team and offered to sell me the competitor’s database.}
  
        \zh{他们通过我们的团队联系到我，提出要卖给我这个倒霉竞争对手的数据库。}
  
        \ja{彼らは私たちのチーム経由で私に接触し、不運な競合のDBを買わないかと持ちかけた。}

  \item \ru{Не получилось – нам это просто не надо.}
  
        \en{It didn’t work—we simply don’t need that.}
  
        \zh{没谈成——我们根本不需要那种东西。}
  
        \ja{うまくいかなかった――そもそも私たちには不要だ。}

  \item \ru{Не уверен, что та сторона была бы настолько же великодушна, но я хакеров послал.}
  
        \en{I’m not sure the other side would have been as magnanimous, but I told the hackers to get lost.}
  
        \zh{我不确定对方会不会这么大度，但我把黑客直接打发走了。}
  
        \ja{相手側が同じくらい寛大だったかは疑わしいが、私はハッカーを追い払った。}

  \item \ru{А теперь в благодарность распространяются байки про то, что «они нас взломали».}
  
        \en{And now, in gratitude, they’re spreading stories that “we hacked them.”}
  
        \zh{而现在，他们的“回报”就是四处散布传言，说“是我们黑了他们”。}
  
        \ja{そして今、その「お礼」として『奴らが俺たちをハックした』という作り話が広まっている。}

  \item \ru{Автор: Данила 4.12.2006, 12:58}
  
        \en{Author: Danila — 2006-12-04 12:58}
  
        \zh{作者：Danila　2006-12-04 12:58}
  
        \ja{投稿者：ダニラ　2006-12-04 12:58}

  \item \ru{Новый проект Павла и Николая Дуровых стартует с криминальной хакерской атаки и плагиата!}
  
        \en{Pavel and Nikolai Durov’s new project launches with a criminal hacking attack and plagiarism!}
  
        \zh{帕维尔和尼古拉·杜罗夫的新项目，竟然是以“犯罪式”的黑客攻击和抄袭起步的！}
  
        \ja{パーヴェルとニコライ・ドゥーロフの新プロジェクトは、犯罪的ハッキング攻撃と盗用でスタートした！}

  \item \ru{КРИМИНАЛ.}
  
        \en{CRIME.}
  
        \zh{犯罪。}
  
        \ja{犯罪。}

  \item \ru{Наш сайт (MoiFakultet.ru) 01.12.06 подвергся криминальной хакерской атаке со стороны команды Павла Дурова.}
  
        \en{Our site (MoiFakultet.ru) on 2006-12-01 was hit by a criminal hacking attack from Pavel Durov’s team.}
  
        \zh{我们的站点（MoiFakultet.ru）在 2006-12-01 遭到帕维尔·杜罗夫团队的“犯罪式”黑客攻击。}
  
        \ja{私たちのサイト（MoiFakultet.ru）は2006-12-01、パーヴェル・ドゥーロフのチームによる犯罪的ハッキング攻撃を受けた。}

  \item \ru{Документальное свидетельство (заказ на взлом сайта) смотрите в Яндекс-блогах:}
  
        \en{For documentary proof (an order to hack the site), see Yandex Blogs:}
  
        \zh{“书面证据”（网站入侵委托）请看 Yandex 博客：}
  
        \ja{証拠資料（サイト侵入の依頼）はYandexブログで確認せよ：}

  \item \ru{\url{http://blogs.yandex.ru/search.xml?how=tm&rd=2&text=moifakultet.ru}}
  
        \en{\url{http://blogs.yandex.ru/search.xml?how=tm&rd=2&text=moifakultet.ru}}
  
        \zh{\url{http://blogs.yandex.ru/search.xml?how=tm&rd=2&text=moifakultet.ru}}
  
        \ja{\url{http://blogs.yandex.ru/search.xml?how=tm&rd=2&text=moifakultet.ru}}

  \item \ru{[сейчас ничего криминального по этой ссылке найти невозможно. – Н. К.].}
  
        \en{[Today you can’t find anything “criminal” at that link. — N.K.]}
  
        \zh{[如今从这个链接已经找不到任何“犯罪证据”了。——N.K.]}
  
        \ja{[現在このリンクから「犯罪的」なものは何も見つからない。――N.K.]}

  \item \ru{Вот цитата текста объявления Павла или его подручного: «Большая просьба проверить два сайта на уязвимость: \_vkontakte.ru и moifakultet.ru}
  
        \en{Here’s a quote from Pavel’s (or his aide’s) post: “Please check two sites for vulnerabilities: \_vkontakte.ru and moifakultet.ru}
  
        \zh{这是帕维尔或其手下发布的公告节选：“请帮忙检查两个网站的漏洞：\_vkontakte.ru 和 moifakultet.ru}
  
        \ja{これがパーヴェル本人、あるいは手下の告知文の引用だ。「お願い：二つのサイトの脆弱性を確認してほしい。\_vkontakte.ru と moifakultet.ru}

  \item \ru{Если найдете во втором сайте серьезные дырки, с меня \$. Заранее спасибо».}
  
        \en{If you find serious holes in the second site, I’ll pay. Thanks in advance.”}
  
        \zh{如果在第二个网站里发现严重漏洞，我给钱。先谢了。”}
  
        \ja{二つ目のサイトで重大な穴を見つけたら、こちらで払う。よろしく」。}

  \item \ru{После этого, 01.12.06, наш сайт был взломан и прекратил работать на 1 сутки…}
  
        \en{After that, on 2006-12-01, our site was hacked and stopped working for a full day…}
  
        \zh{随后在 2006-12-01，我们的网站被黑，瘫痪了整整一天……}
  
        \ja{その後、2006-12-01に私たちのサイトは侵入され、丸一日停止した……}

  \item \ru{Возможно, часть мейлов был похищена и будет в дальнейшем использована для увеличения аудитории сайта вконтакте.ру.}
  
        \en{It’s possible some emails were stolen and will later be used to grow vkontakte.ru’s audience.}
  
        \zh{可能有一部分邮箱被盗，今后会被用来给 vkontakte.ru 拉新。}
  
        \ja{メールアドレスの一部が盗まれ、今後vkontakte.ruの利用者拡大に使われる可能性がある。}

  \item \ru{ПЛАГИАТ.}
  
        \en{PLAGIARISM.}
  
        \zh{抄袭。}
  
        \ja{盗用。}

  \item \ru{До хакерской атаки Павел с братом отличились тем, что оперативно скопировали наш сайт.}
  
        \en{Before the hack, Pavel and his brother had already distinguished themselves by quickly copying our site.}
  
        \zh{在黑客攻击之前，帕维尔和他弟弟就“干得漂亮”——他们迅速抄了我们的网站。}
  
        \ja{ハッキングの前から、パーヴェルと弟は私たちのサイトを素早くコピーするという「実績」を作っていた。}

  \item \ru{Убедиться в этом также просто: достаточно посмотреть на дату регистрации нашего сайта: (domain: MOIFAKULTET.RU, created: 2006.08.14) и на дату регистрации}
  
        \en{It’s easy to verify: just look at our site’s registration date (domain: MOIFAKULTET.RU, created: 2006.08.14) and the registration date of…}
  
        \zh{要验证也很简单：看看我们网站的注册日期（domain: MOIFAKULTET.RU, created: 2006.08.14），再看看对方的注册日期就知道了——}
  
        \ja{確認は簡単だ。私たちのサイトの登録日（domain: MOIFAKULTET.RU, created: 2006.08.14）と、相手側の登録日を見ればいい――}

  \item \ru{…}
  
        \en{[Continues on next page]}
  
        \zh{（下页续）}
  
        \ja{（次ページへ続く）}
\end{itemize}

\end{document}

